---
title: "Spatial Synchrony at High Resolutions"
output: pdf_document
---


<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
if (!dir.exists("./.checkpoint/")){
  dir.create("./.checkpoint/")
}
checkpoint("2020-04-26",checkpointLocation = "./")
```

\section{Prereqs - R Libraries}
Ensure you have all libraries listed below:
```{r, echo = FALSE}
#require("tseries")
#require("stargazer")
#require("fmsb")
#require("sjmisc")
#require("pracma")
#require("SpatialPack")
```

Sourcing scripts:
```{r sourcing_files, echo = FALSE}
source("./scripts/mtime.R")
```

\section{Data Generation}
We first need to generate the data for the analysis.
```{r data_generator, echo=F}
source("scripts/AVHRRDataGenerator.R")
AVHRRDataGenerator(force = F)
```
You can control the variable force to control whether or not you wish to recreate all csv/RDS files (TRUE) or just csv/RDS files you do not have (FALSE).

\section{Statistics}

Creates linear models and more accurate spatial stats for all the drivers.
```{r get_statistics, echo=F, cache=T,cache.extra=list(mtime("scripts/AVHRRStatistics.R"),mtime("scripts/VectorizeMatrices.R"),mtime("scripts/ModelScene.R"),mtime("scripts/SpatialMatrixSignificance.R"),mtime("scripts/SpatiallyCorrectedModels.R"))}
source("scripts/AVHRRStatistics.R")
AVHRRStatistics()
```

```{r print_statistics_linermodel, echo=F}
source("scripts/get_summary_table_for_lm_VIF.R")

all_lm_VIF_res<-readRDS("data/csvFiles/all_lm_VIF_res.RDS")
get_summary_table_for_lm_VIF(all_lm_VIF_res,targetzone="interior",type="text")
get_summary_table_for_lm_VIF(all_lm_VIF_res,targetzone="desert",type="text")
get_summary_table_for_lm_VIF(all_lm_VIF_res,targetzone="coastal",type="text")
```

```{r get_plot_spatiallycorrectedmodel, echo=F, results="hide"}
#--------Interpret Spatially corrected model-results: plots to be saved in the figures/ folder ------------
if(!dir.exists("./figures")){
  dir.create("./figures")
}

# Plotter function to generate multipanel pdf plots to interpret Spatially corrected model-results
# Args: 
# res = output list of length two (corr and pval) from Spatial corrected model statistics
# nametag = a character vector
# plotlegend = logical, default=F

Spatial_corrected_res_plotter<-function(res,nametag,plotlegend=F){
  
  res_cor<-res[[1]]
  res_p<-res[[2]]
  
  rn<-rownames(res_cor)
  res_cor$City<-res_p$City<-sub('_.*$','', rn)
  colnames(res_cor)<-c("Temp_avg_NDVI","Population","Agriculture","Development","Elevation","Slope","City")
  colnames(res_p)<-c("p.Temp_avg_NDVI","p.Population","p.Agriculture","p.Development","p.Elevation","p.Slope","City")
  
  res_cor<-as.matrix(res_cor)
  res_p<-as.matrix(res_p)
  
  pdf(paste("./figures/Spatially_corrected_model_results_modifiedttest_",nametag,".pdf",sep=""),height=5,width=9)
  op<-par(mar=c(3,3,1,1),mgp=c(3,1,0),mfcol=c(4,3),oma=c(2,2,0,0))
  for(i in 1:nrow(res_cor)){
    plot(res_p[i,1:6],res_cor[i,1:6],
         xlim=c(0,1),ylim=c(-1,1),
         col="black",bg=rainbow(6),pch=21,
         xlab="",ylab="",cex.lab=2)
    abline(h=0,col="grey")
    abline(v=0.1)
    abline(v=0.05,lty="dashed")
    abline(v=0.01,lty="dotted")
    legend("topright",res_p[i,7],bty="n")
  }
  mtext("correlation coefficient", side=2, line=47, adj=-1.5)
  mtext("p-value", side=1, line=2.8, adj=-1.2)
  par(op)
  dev.off()
  
  if(plotlegend==T){
    pdf(paste("./figures/Spatially_corrected_model_results_modifiedttest_legend.pdf",sep=""),height=1,width=16)
    op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
    plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
    legend("center", legend = colnames(res_cor)[1:6], pch=21, pt.bg=rainbow(6),
           x.intersp = 0.2,
           cex = 1.8, xpd = TRUE, horiz = T, inset = c(0,0), 
           bty = "n")
    par(op)
    dev.off()
  }
  
}

# call the plotter function
res<-readRDS("data/csvFiles/AVHRR_PearsonCorrelationData.RDS")
Spatial_corrected_res_plotter(res=res,nametag="pearson",plotlegend=T)

res<-readRDS("data/csvFiles/AVHRR_SpearmanCorrelationData.RDS")
Spatial_corrected_res_plotter(res=res,nametag="spearman",plotlegend=F)

res<-readRDS("data/csvFiles/AVHRR_PearsonNo2010CorrelationData.RDS")
Spatial_corrected_res_plotter(res=res,nametag="pearson_no2010",plotlegend=F)

res<-readRDS("data/csvFiles/AVHRR_SpearmanNo2010CorrelationData.RDS")
Spatial_corrected_res_plotter(res=res,nametag="spearman_no2010",plotlegend=F)

# Shya's Comments:
# I personally think, excluding 2010 has no significant difference in model prediction.
# I also think to compare between different cities within each category: like between Las Vegas and Pheonix (both Desert cities),
# we should consider same scan area (the model scene) around the target city to get which predictor is significant?
```    

\section{Exploratory Map Analysis}
```{r get_model_scenes, echo=F, message=F, cache=T,cache.extra=list(mtime("scripts/GenerateMaps.R"),mtime("scripts/AVHRRDataGenerator.R"),mtime("scripts/MapCreator_wrapper.R"),mtime("scripts/MapCreator.R"),mtime("scripts/MatrixToDataFrame.R"))}
source("scripts/GenerateMaps.R")
```
This code should create ggplot2 maps of some of the data in R. Good to visualize results in AVHRR coordinates before spending time converting to Arc.

\section{Next Steps}
You now have all the data, the statistics, and some R maps for the scenes. You can now do several things:

\begin{enumerate}
	\item Create Lat/Lon Maps. You need to run NaToNaN.R then CSVToBIL.m to get the correct files. Then you can load in the data into a GIS system. Note that template.hdr will
	ensure that the data is projected correctly.
	\item Add new scenes in AVHRRStatistics.R
	\item Add new data in AVHRRDataGenerator.R
\end{enumerate} 
