---
title: "Spatial Synchrony at High Resolutions"
output:
  html_document:
    df_print: paged
---

\section{Prereqs - R Libraries}
Ensure you have all libraries listed below:
```{r, echo = FALSE}
require("matlabr")
require("tseries")
require("stargazer")
require("fmsb")
require("sjmisc")
```

Sourcing scripts:
```{r, echo = FALSE}
source("scripts/AVHRRDataGenerator.R")
source("scripts/AVHRRStatistics.R")
```

\section{Data Generation}
We first need to generate the data for the analysis. 

```{r}
AVHRRDataGenerator(force = FALSE)
```
You can control the variable force to control whether or not you wish to recreate all csv files (TRUE) or just csv files you do not have (FALSE).

\section{Statistics}
```{r}
AVHRRStatistics()
```

\section{Exploratory Mapping}
```{r}
source("scripts/GenerateMaps.R")
```
This section generates ggplot2 maps of the data, including synchrony. Notice that these maps are not in Lat/Lon coordinates, but are in fact in AVHRR coordinates. This function is mainly used to generate exploratory maps before putting in the effort to create polished GIS type maps.

\section{Next Steps}
At this point, you now have all the data and statistics for this project. There are some things you can now do with this information:

\begin{enumerate}
  \item Alter AVHRRStatistics/GenerateMaps with new scenes.
  \item Alter AVHRRDataGenerator to include more kinds of data.
  \item Create Geographically accurate maps using NaToNaN.R then CSVtoBIL.m. This will create Bil files for ArcMap. There will be a 
  template.hdr that will ensure the correct projections for the data.
\end{enumerate}
