---
title: "Spatial Synchrony at High Resolutions"
output:
  html_document:
    df_print: paged
---

\section{Prereqs - R Libraries}
Ensure you have all libraries listed below:
```{r, echo = FALSE}
require("tseries")
require("stargazer")
require("fmsb")
require("sjmisc")
require("pracma")
require("SpatialPack")
```

Sourcing scripts:
```{r, echo = FALSE}
source("scripts/AVHRRDataGenerator.R")
source("scripts/AVHRRStatistics.R")
```

\section{Data Generation}
We first need to generate the data for the analysis.
```{r}
AVHRRDataGenerator(force = FALSE)
```
You can control the variable force to control whether or not you wish to recreate all csv files (TRUE) or just csv files you do not have (FALSE).

\section{Statistics}
Creates linear models and more accurate spatial stats for all the drivers.
```{r}
#AVHRRStatistics()
```

\section{Exploratory Map Analysis}
```{r}
#source("scripts/GenerateMaps.R")
```
This code should create ggplot2 maps of some of the data in R. Good to visualize results in AVHRR coordinates before spending time converting to Arc.

\section{Next Steps}
You now have all the data, the statistics, and some R maps for the scenes. You can now do several things:

\begin{enumerate}
	\item Create Lat/Lon Maps. You need to run NaToNaN.R then CSVToBIL.m to get the correct files. Then you can load in the data into a GIS system. Note that template.hdr will
	ensure that the data is projected correctly.
	\item Add new scenes in AVHRRStatistics.R
	\item Add new data in AVHRRDataGenerator.R
\end{enumerate} 
